Syntax and Semantics of Abstract Binding Trees

### 2015-12-12 paper.tex
typo

The representation of telescopes and sequents in a logical framework is
notoriously difficult; whilst it is possible to use higher-order abstract
syntax or abts to encode the binding-structure of telescopes and sequents, the
encoding is sufficiently laborious and obscure that it is not used in practice.
Crary has demonstrated a first-order encoding of contexts in the logical
framework in bijection with actual LF-contexts~\cite{crary:2009}, which has
been successfully used in large-scale mechanization efforts, including that of
Standard ML~\cite{lee-crary-harper:2007} and the Edinburgh Logical Framework
itself~\cite{martens-crary:2012}.

@@

\begin{remark}
  In the full development of a theory of behavioral refinements, the ad-hoc
  judgment $\IsWf{\Upsilon}{\Gamma}{M}{\tau}$ would be replaced with a general
  notion of refinement $\IMode{\phi}\sqsubset\tau$ ($\phi$ refines sort
  $\tau$), and a new judgment $\IMode{\Upsilon}\parallel\IMode{\Phi}\vDash
  \IMode{M} \in \IMode{\phi}$, such that $\phi$ refines $\tau$ the
  refinement context $\Phi$ refines some sort context $\Gamma$. Furthermore, in
  addition to restricting membership, refinements might also be designed to
  coarsen equivalence.
\end{remark}

>>>>

The representation of telescopes and sequents in a logical framework is
notoriously difficult; whilst it is possible to use higher-order abstract
syntax or abts to encode the binding-structure of telescopes and sequents, the
encoding is sufficiently laborious and obscure that it is not used in practice.
Crary has demonstrated a first-order encoding of contexts in the Edinburgh
Logical Framework (ELF) in bijection with actual LF-contexts~\cite{crary:2009},
which has been successfully used in large-scale mechanization efforts,
including that of Standard ML~\cite{lee-crary-harper:2007} and the ELF
itself~\cite{martens-crary:2012}.

@@

\begin{remark}
  In the full development of a theory of behavioral refinements, the ad-hoc
  judgment $\IsWf{\Upsilon}{\Gamma}{M}{\tau}$ would be replaced with a general
  notion of refinement $\IMode{\phi}\sqsubset\tau$ ($\phi$ refines sort
  $\tau$), and a new judgment $\IMode{\Upsilon}\parallel\IMode{\Phi}\vDash
  \IMode{M} \in \IMode{\phi}$, such that $\phi$ refines $\tau$ and the
  refinement context $\Phi$ refines some sort context $\Gamma$. Furthermore, in
  addition to restricting membership, refinements might also be designed to
  coarsen equivalence.
\end{remark}
